{\large Gravitational wave sources in our Galactic backyard:}\\{\normalsize Predictions for BHBH, BHNS and NSNS binaries in LISA

### 2021-09-28 paper/tex/paper.tex
WR wind text and more

\usepackage{lipsum}
\usepackage{physics}
\usepackage{multirow}
\usepackage{xspace}
\usepackage{natbib}
\usepackage{fontawesome5}
\usepackage{xcolor} % to add more color options
\usepackage{wrapfig}

@@

\acknowledgments{We thank Mike Lau, Floris Kummer, Eva Laplace, Rob Farmer, Katie Sharpe, Mathieu Renzo, Katie Brevik, Alberto Sesana, Valeriya Korol, Will Farr, Tyson Littenberg and the members of the COMPAS collaboration for insightful discussions. TW also thanks Terence Lovatt for his advice and help on improving an earlier draft of this project. This project was funded in part by the European Union’s Horizon 2020 research and innovation program from the European Research Council (ERC, Grant agreement No. 715063), and by the Netherlands Organization for Scientific Research (NWO) as part of the Vidi research program BinWaves with project number 639.042.728. We further acknowledge the Black Hole Initiative funded by a generous contribution of the John Templeton Foundation and the Gordon and Betty Moore Foundation.}

>>>>

\usepackage{lipsum}
\usepackage{physics}
\usepackage{multirow}
\usepackage{xspace}
\usepackage{natbib}
\usepackage{fontawesome5}
\usepackage{xcolor} % to add more color options
\usepackage{wrapfig}
\usepackage{tabularx}
\usepackage[figuresright]{rotating}

@@

\acknowledgments{We thank Mike Lau, Floris Kummer, Eva Laplace, Rob Farmer, Katie Sharpe, Mathieu Renzo, Katie Brevik, Alberto Sesana, Valeriya Korol, Will Farr, Tyson Littenberg and the members of the COMPAS collaboration for insightful discussions. TW also thanks Terence Lovatt for his advice and help on improving an earlier draft of this project. This project was funded in part by the National Science Foundation under Grant No. (NSF grant number 2009131), the European Union’s Horizon 2020 research and innovation program from the European Research Council (ERC, Grant agreement No. 715063), and by the Netherlands Organization for Scientific Research (NWO) as part of the Vidi research program BinWaves with project number 639.042.728. We further acknowledge the Black Hole Initiative funded by a generous contribution of the John Templeton Foundation and the Gordon and Betty Moore Foundation.}

### 2021-09-28 paper/tex/sections/methods.tex

Although \citet{Frankel+2018} only fit this model for the low-\achem~disc, we also use this metallicity-radius-time relation for the high-$\alpha$ disc and the bar, but focusing on the chemical tracks more representative to the inner disc and large ages. \citet{Sharma+2020} showed that using a simple continuous model for both the low- and high-\achem~discs, the Milky Way abundance distributions could be well reproduced. Empirically, the abundance tracks in the [$\alpha$/Fe]-[Fe/H] plane of the stars in the bulge/bar follow the same track as those of the old stars in the Solar neighbourhood \citep[][Fig.~7,]{Bovy+2019}, which motivates our modelling choice to use the same metallicity-radius-time relation.

>>>>

Although \citet{Frankel+2018} only fit this model for the low-\achem~disc, we also use this metallicity-radius-time relation for the high-$\alpha$ disc and the bar, but focusing on the chemical tracks more representative to the inner disc and large ages. \citet{Sharma+2020} showed that using a simple continuous model for both the low- and high-\achem~discs, the Milky Way abundance distributions could be well reproduced. Empirically, the abundance tracks in the [$\alpha$/Fe]-[Fe/H] plane (and other elements) of the stars in the bulge/bar follow the same track as those of the old stars in the Solar neighbourhood \citep[][Fig.~7,]{Griffith+2021,Bovy+2019}, which motivates our modelling choice to use the same metallicity-radius-time relation.
